An Investigation of Confusing Code Patterns in JavaScript

### 2022-12-14 discussion.tex
review os s04

In the repeated measures study, we identified one JavaScript-specific atom, Object Destructuring. In the Latin square study, Automatic Semicolon Insertion was identified as another JavaScript-specific atom. For both cases, p-values were much lower than the threshold and effect sizes were high. However, in the repeated measures study obfuscated versions of Automatic Semicolon Insertion were not significantly different from their clean counterparts. Our interviewees favored the use of semicolon over Automatic Semicolon Insertion. Finally, as discussed in Section~\ref{sec:repeated:correct}, Array Destructuring exhibited a large effect size, in spite of the non-statistically significant difference (after correction). As discussed elsehwere~\cite{Ellis:2010:EGE}, this is a scenario that hints at practical relevance, specially considering the very low p-value ($< 0.003$). Further studies investigating these code patterns, potentially using different response variables~\cite{Oliveira:2020:ECR,Feitelson:2021:CPC}, are left for future work.

@@

\castor{For the pros and cons of each approach, do you prefer lists of items or regular text paragraphs?}
\revised{The experimental designs we have employed in the two experiments have different trade-offs. The main advantages of having a repeated measures (or within subjects) study are the following: 
\begin{itemize}
  \item[+] They are better able to detect an effect size, given that one exists, since it is possible to collect data about both treatments from each participant. 
  \item[+] There tends to be less variance between groups, since the same participant is subject to both treatments
  \item[+] Individual differences between participants are controlled for because each participant acts as their own control
\end{itemize}
}
\revised{
\noindent
Conversely, the main limitations of a repeated measures study are the following: 
\begin{itemize}
\item[--] Data is not independent. This precludes the use of some statistical techniques and tests. 
\item [--] There is a potential learning/practice effect, since going through multiple examples may make the participants able to predict results of subsequent cases. This can be mitigated by separating examples pertaining to the same atom candidate, but not eliminated. 
\item [--] Fatigue effect, since participants have to examine more code snippets. This was exacerbated in our case, due to the larger number of atom candidates.
\end{itemize}}
\revised{
The Latin square study is an example of a between subjects study. In a way, its main advantages are precisely the absence (or a reduction) of the disadvantages of the repeated measures study and its main disadvantages are related to the advantages of a repeated measures study: 
\begin{itemize}
\item[+] Data is independent. 
\item[+] There is no possibility of learning/practice effect and the fatigue effect is reduced since each participant is only exposed to one version of each code snippet. There is no possibility of learning/practice effect because each participant is only exposed to one treatment.  
\end{itemize}}
\revised{
\noindent
The main disadvantages of a between subjects study are the following:
\begin{itemize}
  \item[-] Effect sizes tend to be lower. 
  \item[-] Does not account for variance within groups.
\end{itemize}
The use of a Latin square mitigates some of the disadvantages intrinsic to a between subjects design. For example, since less work is required from participants, it was possible to obtain more data for the latin square study than we could get for the repeated measures study. This increases its statistical power, making it possible to detect smaller effect sizes.}

>>>>

In the repeated measures study, we identified one JavaScript-specific atom, Object Destructuring. In the Latin square study, Automatic Semicolon Insertion was identified as another JavaScript-specific atom. For both cases, p-values were much lower than the threshold and effect sizes were high. However, in the repeated measures study obfuscated versions of Automatic Semicolon Insertion were not significantly different from their clean counterparts. Our interviewees favored the use of semicolon over Automatic Semicolon Insertion. Finally, as discussed in Section~\ref{sec:repeated:correct}, Array Destructuring exhibited a large effect size, in spite of the non-statistically significant difference (after correction). As discussed elsewhere~\cite{Ellis:2010:EGE}, this is a scenario that hints at practical relevance, especially considering the very low p-value ($< 0.003$). Further studies investigating these code patterns, potentially using different response variables~\cite{Oliveira:2020:ECR,Feitelson:2021:CPC}, are left for future work.

@@

% \castor{For the pros and cons of each approach, do you prefer lists of items or regular text paragraphs?}
\revised{The experimental designs we have employed in the two experiments have different trade-offs. The main advantages of having a repeated measures (or within subjects) study are the following: 
\begin{itemize}
  \item[+] They are better able to detect an effect size, given that one exists, since it is possible to collect data about both treatments from each participant. 
  \item[+] There tends to be less variance between groups, since the same participant is subject to both treatments
  \item[+] Individual differences between participants are controlled for because each participant acts as their own control
\end{itemize}
}
\revised{
\noindent
Conversely, the main limitations of a repeated measures study are the following: 
\begin{itemize}
\item[--] Data is not independent. This precludes the use of some statistical techniques and tests. 
\item [--] There is a potential learning/practice effect, since going through multiple examples may make the participants able to predict results of subsequent cases. This can be mitigated by separating examples pertaining to the same atom candidate, but not eliminated. 
\item [--] Fatigue effect, since participants have to examine more code snippets. This was exacerbated in our case, due to the larger number of atom candidates.
\end{itemize}}
\revised{
The Latin square study is an example of a between subjects study. In a way, its main advantages are precisely the absence (or a reduction) of the disadvantages of the repeated measures study and its main disadvantages are related to the advantages of a repeated measures study: 
\begin{itemize}
\item[+] Data is independent. 
\item[+] There is no possibility of learning/practice effect and the fatigue effect is reduced since each participant is only exposed to one version of each code snippet. There is no possibility of learning/practice effect because each participant is only exposed to one treatment.  
\end{itemize}}
\revised{
\noindent
The main disadvantages of a between subjects study are the following:
\begin{itemize}
  \item[-] Effect sizes tend to be lower. 
  \item[-] Does not account for variance within groups.
\end{itemize}
The use of a Latin square mitigates some of the disadvantages intrinsic to a between subjects design. For example, since less work is required from participants, it was possible to obtain more data for the latin square study than we could get for the repeated measures study. This increases its statistical power, making it possible to detect smaller effect sizes.}
